The spread of COVID-19 in a landlocked country the case of Luxembourg

### 2021-03-14 paper/paper.Rmd
update but incomplete week of the 8th of March

---
title: The spread of COVID-19 in a landlocked country the case of Luxembourg
authors:
  - name: Bruno Rodrigues
    thanks: This preprint was written during my free time as a private citizen, and reflects in no manner the views of the Ministry of Higher Education and Research, nor the Government of the Grand-Duchy of Luxembourg.
    department: Statistics department
    affiliation: Ministry of Higher Education and Research, Grand-Duchy of Luxembourg
    location: Luxembourg, 18-20, Montée de la Pétrusse
    email: bruno.rodrigues@mesr.etat.lu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

>>>>

---
title: The spread of COVID-19 in a landlocked country the case of Luxembourg
authors:
  - name: Bruno Rodrigues
    thanks: This preprint was written during my free time as a private citizen, and reflects in no manner the views of the Ministry of Higher Education and Research, nor the Government of the Grand-Duchy of Luxembourg.
    department: Statistics department
    affiliation: Ministry of Higher Education and Research, Grand-Duchy of Luxembourg
    location: Luxembourg, 18-20, Montée de la Pétrusse
    email: bruno.rodrigues@mesr.etat.lu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: bibliography.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---
